Genome-wide changes in expression during inflorescence architecture development

### 2015-09-16 ms.Rmd
fixes #8

**`r I(pasteLabel("Figure ", figCount, "f_madsTree"))`**. Neighbour-joining similarity tree of putatative MIKC proteins in *A. thaliana*, *Solanum lycopersicum* and *Oryza sativa* ssp. *japonica*. Named proteins starting with AT_ or OS_ are from Arabidopsis or rice respectively, and other proteins are labelled with their unique identifiers. The colour of the label represents the Log~2~-fold change (L~2~FC) in expression of the gene encoding that protein between undifferentiated and differentiated meristems. A white background indicates that no results were returned by `DESeq2` for the gene in question, *e.g.* because of low read counts or an extreme count outlier. For rice, L~2~FC was estimated from the RM and SM samples reported here. For *A. thaliana*, L~2~FC was estimated using the inflorescence meristem and floret meristem samples reported by @Mantegazza:2014di. The simpodial meristem and floret meristem samples generated by @Park:2012dg were used to estimate L~2~FC values for tomato genes. Clades are labelled following the nomenclature presented by (**ref: Arora paper**).

>>>>

**`r I(pasteLabel("Figure ", figCount, "f_madsTree"))`**. Neighbour-joining similarity tree of putatative MIKC proteins in *A. thaliana*, *Solanum lycopersicum* and *Oryza sativa* ssp. *japonica*. Named proteins starting with AT_ or OS_ are from Arabidopsis or rice respectively, with synonyms in parentheses, and other proteins are labelled with their unique identifiers. The colour of the label represents the Log~2~-fold change (L~2~FC) in expression of the gene encoding that protein between undifferentiated and differentiated meristems. A white background indicates that no results were returned by `DESeq2` for the gene in question, *e.g.* because of low read counts or an extreme count outlier. For rice, L~2~FC was estimated from the RM and SM samples reported here. For *A. thaliana*, L~2~FC was estimated using the inflorescence meristem and floret meristem samples reported by @Mantegazza:2014di. The simpodial meristem and floret meristem samples generated by @Park:2012dg were used to estimate L~2~FC values for tomato genes. Clades are labelled following the nomenclature presented by (**ref: Arora paper**).
